Supplementary Information

### 2015-06-22 manuscript/coverletter.tex
Second try on coverletter

We are happy to invite you to consider our manuscript 
``\mytitle'' for publication in the Theoretical Biology section of the \emph{\myjournal}.

>>>>

We are happy to invite you to consider our manuscript 
``\mytitle'' for publication in the Population and Community Ecology section of the \emph{\myjournal}.

Our study aims to combine two well-established but disparate ecological themes, namely the analysis of macroecological gradients and the search for general laws governing the structure of communities, as measured through food webs (networks of who eats whom). In particular, we were interested in the possibility of a link between the well-known latitudinal gradients in species richness of some taxa (e.g., birds, land plants) and the scaling relationships between species richness and food-web structure. With regard to the former, one  hypothesized mechanism for greater species richness in the tropics is the latitude-niche-breadth hypothesis, which predicts that the greater stability of temperature and productivity in the tropics will permit species to evolve narrower niches and therefore more finely partition habitats. If this hypothesis holds true, then tropical species should be more specialized than their high-latitude counterparts.

In terms of a food web, this means that we would naively expect that tropical species will have relatively fewer feeding links than polar species. However, the number of feeding links in which a species is involved is known to scale with the number of species in the community food web following a power law. Therefore we also expect that species in tropical food webs will participate in many feeding links by virtue of their speciose communities. This apparent paradox can be resolved by adding an effect of latitude to the exponent of the power law. We tested for the impact of such an exponent, as well as potential interactions between the effects of latitude and ecosystem type on scaling laws.

We found that, in general, there was little effect of latitude on scaling relationships between diet breadth and species richness. If diet breadth may be taken as a measure of a species' Eltonian (biotic) niche, this means that our results are inconsistent with the latitude-niche-breadth hypothesis. Ecosystem type, on the other hand, had a greater impact on scaling exponents, suggesting that different processes may structure food webs in different habitats.

Our results are the pinnacle of interestingness and you should publish them before we decide to give them to Nature instead. Everyone will love us and then the world will shower me with options for my future. That's how this works, right?
